---
title: "Workflow Statistics"
output: pdf_document
---

```{r echo=FALSE}
library(scales)
library(reshape2)
library(ggplot2)
```

## Statistics on Worker Nodes
```{r echo=FALSE}
workers <- read.csv('csv_files/worker_nodes.csv', header=TRUE, sep=',')
workers$MIPS <-as.numeric(sub("Mf", "", workers$MIPS))
```

### Distibution of Worker Nodes by Country

```{r echo=FALSE, fig.height=3.5}
ggplot(workers, aes(factor(Country))) + geom_bar(aes(fill= ..count..)) + guides(fill=FALSE) +
    xlab("Country") + ylab("Number of worker nodes")
```

### With a split by number of cores

```{r echo=FALSE, fig.height=4}
ggplot(workers, aes(x=Country, fill=factor(Core))) + geom_bar() + scale_fill_discrete(name="#Cores") +
  xlab("Country") + ylab("Number of worker nodes") + theme(legend.position="top")
```

### Split by BogoMIPS and Country

```{r echo=FALSE, fig.height=3.5}
ggplot(workers, aes(x=round(MIPS, -2), fill=factor(Country))) + geom_bar(binwidth=100) +
  xlab("BogoMIPS") + ylab("Number of worker nodes")+ scale_fill_discrete(name="Country") +
  theme(legend.position="top")
```

### CloseSE vs. Grid Site by country

```{r echo=FALSE, fig.height=5.25}
workers$SESuffix<-sapply(workers$CloseSE, function(x) tail(strsplit(as.character(x),"[.]")[[1]], n=1))
ggplot(workers,aes(x=SiteName, y=CloseSE)) + geom_point()+ facet_grid(SESuffix~Country, scales="free") +
  theme(axis.text.x = element_text(angle = 50, hjust = 1)) + xlab("Grid Site") 
```

### Distribution of Worker nodes by Grid Site

```{r echo=FALSE, fig.height=4}
ggplot(workers, aes(factor(SiteName))) + geom_bar(aes(fill= ..count..)) + guides(fill=FALSE) + 
  facet_wrap(~Country, scales="free_x", nrow=1) + theme(axis.text.x = element_text(angle = 50, hjust = 1)) + 
  xlab("Grid Site") + ylab("Number of worker nodes")
```

### With a split by number of cores

```{r echo=FALSE, fig.height=4.75}
ggplot(workers, aes(x=SiteName, fill=factor(Core))) + geom_bar() + scale_fill_discrete(name="#Cores") + 
  facet_wrap(~Country, scales="free_x", nrow=1) + theme(axis.text.x = element_text(angle = 50, hjust = 1)) + 
  xlab("Grid Site") + ylab("Number of worker nodes") + theme(legend.position="top")
```

## Statistics on file transfers
```{r echo=FALSE}
transfers <- read.csv('csv_files/file_transfer.csv', header = TRUE, sep=',')

# Remove entry with 0 file size
transfers = transfers[transfers$FileSize!=0,]

# Simplify the job IDs
transfers$JobId <- transfers$JobId-min(transfers$JobId)

# Remove the upload that corresponds to the number of particules made by the Merge job
uploads <- transfers[transfers$FileSize > 20 & transfers$UpDown == 1,]
```
### Distribution of Upload Test durations (in milliseconds)
```{r echo=FALSE}
upload_tests <- transfers[transfers$UpDown == 0,]
upload_tests$src_suffix<-sapply(upload_tests$Source, function(x) tail(strsplit(as.character(x),"[.]")[[1]], n=1))
upload_tests$dst_suffix<-sapply(upload_tests$Destination, function(x) tail(strsplit(as.character(x),"[.]")[[1]], n=1))

upload_tests$short_long = 
  sapply(upload_tests$Time, function(x) if (x > 1500) {"Long"} else {"Short"})
# Have the facet in the logical order rather than in the alphabetical one
upload_tests$short_long = factor(upload_tests$short_long, levels = c("Short", "Long"))
```
```{r echo=FALSE}
summary(upload_tests$Time)
```

### By Job Id
```{r echo=FALSE,fig.height=3.25}
ggplot(upload_tests, aes(x=JobId, y=Time)) + geom_point() + 
  facet_wrap(~short_long, scales="free_y") + 
  ylab ("Duration (in milliseconds)") + xlab ("Job ID")
```

### By Destination (darkness represents frequency)
```{r echo=FALSE,fig.height=4}
ggplot(upload_tests, aes(x=Time, y=Destination)) + geom_point(alpha=0.2, size=3) +
  theme(axis.text.x = element_text(angle = 50, hjust = 1)) + #theme_bw() +
  xlab ("Duration (in milliseconds)") + facet_grid(dst_suffix~., scales="free")
```

### Impact of Source and Destination countries on "Long" Upload Tests
```{r echo=FALSE}
ggplot(upload_tests[upload_tests$short_long == "Long",], 
       aes(x=Source, y=Destination, color=factor(Time),size=factor(Time))) + 
  geom_point() + facet_grid(src_suffix~dst_suffix, scales="free") +
  scale_color_discrete(name="Duration") + scale_size_discrete(name="Duration") + 
  theme(axis.text.x = element_text(angle = 50, hjust = 1))
```

\newpage

### Distribution of Download durations (in seconds)
```{r echo=FALSE}
downloads <- transfers[transfers$UpDown == 2,]
# Convert durations in seconds 
downloads$Time<-downloads$Time/1000
```
```{r echo=FALSE}
summary(downloads$Time)
```

### blah
```{r echo=FALSE,fig.height=8}
ggplot(downloads, aes(x=JobId, y=Source, size=Time)) + geom_point() + 
  scale_size_continuous(name="Duration", breaks=c(seq(0,40,by=10), 
                                                  seq(50, max(round(downloads$Time)), 
                                                      by=50)), 
                        range=c(1,6)) +
  facet_wrap(~FileSize, ncol=1, scales="free_y") + 
  ylab ("Source SE") + xlab ("Job ID")

```

### blah
```{r echo=FALSE,fig.height=8}
ggplot(downloads, aes(x=JobId, y=factor(FileSize), size=Time)) + geom_point() + 
  scale_size_continuous(breaks=c(seq(0, max(round(downloads$Time)), 
                                     by=50)), 
                        range=c(1,6), name="Duration") +
  facet_wrap(~Source, ncol=1, scales="free_y") + 
  ylab ("File Size (in Bytes)") + xlab ("Job ID")

```

\newpage

```{r}
bandwidths <-read.csv('csv_files/se_bandwidth.csv', header=TRUE, sep=',')
timings <- read.csv('timings/real_times.csv', header = TRUE, sep = ',') 

```


